Supporting Information for\\ ``A weakly structured stem for human origins in Africa''

### 2023-01-06 supplement.tex
final continuous wo stem mig best fit values

\begin{table}[ht]
\caption{
    \label{tab:supp-continuous-migration-no-mig}
    \textbf{Best-fit parameters from the Continuous-Migration model without stem migration.}
    Inferred values are scaled to physical units assuming a generation time of
    29 years. This model gave a log-likelihood of -126,644. This model allows for
    continuous migration between Stem 2 and contemporary populations, but disallows
    migration between Stem 2 and Stem 1, which later splits into branches leading
    to South, East, and West African populations.
}
\centering
\begin{tabular}[t]{rP{8cm}cc}
    \toprule
    Parameter & Description & Value & 95\% CIs \\
    \midrule
    $N_e$ & Ancestral effective population size & 10543 & 10810--11260 \\
    $N_{stem1}$ & Size of stem 1 lineage between Neanderthal and Nama splits & 15297 & 13930--15330 \\
    $N_{stem2}$ & Size of stem 2 lineage & 9156 & 9780--11250 \\
    $N_{Nama_0}$ & Initial Nama size & 11329 & 10760--11280 \\
    $N_{Nama_F}$ & Final Nama size & 219 & 216--226 \\
    $N_{MSL_0}$ & Initial Mende size & 11187 & 10510--11090 \\
    $N_{MSL_F}$ & Final Mende size & 24056 & 24050--25780 \\
    $N_{EA}$ & Size of East African branch & 7185 & 6970--7200 \\
    $N_{Gumuz_F}$ & Final Gumuz size & 3746 & 2650--3860 \\
    $N_{EP}$ & East African agriculturist size & 13187 & 12830--13250 \\
    $N_{GBR_0}$ & Initial British size & 937 & 931--964 \\
    $N_{GBR_F}$ & Final British size & 11478 & 11320--11760 \\
    $N_{Neand}$ & Neanderthal size & 2285 & 2140--2450 \\
    $T_{stems}$ & Stem split time (years) & 459720 & 446600--463300 \\
    $T_{Nama}$ & Nama split time (years) & 139725 & 137300--146000 \\
    $m_{Nama-MSL}$ & Nama--Mende symmetric migration rate & $1.93\times10^{-5}$ & $1.36\times10^{-5}$--$1.81\times10^{-5}$ \\
    $m_{Nama-EA}$ & Nama--East Africa symmetric migration rate & $4.43\times10^{-5}$ & $4.08\times10^{-5}$--$4.60\times10^{-5}$ \\
    $m_{MSL-EA}$ & Mende--East Africa migration rate & $20.8\times10^{-5}$ & $20.7\times10^{-5}$--$21.3\times10^{-5}$ \\
    $m_{EA-GBR}$ & East Africa--Europe migration rate & $4.46\times10^{-5}$ & $4.19\times10^{-5}$--$4.58\times10^{-5}$ \\
    $m_{EA-EA}$ & Intra-East Africa migration rate & $35.4\times10^{-5}$ & $34.6\times10^{-5}$--$37.0\times10^{-5}$ \\
    $f_{GBR \rightarrow EP}$ & Ancestry proportion of East African agriculturalists from GBR 12ka ($1-f$ from Gumuz) & 0.649 & 0.644--0.660 \\
    $f_{EP \rightarrow Nama}$ & Ancestry proportion from EA pastoralists to Nama 2ka & 0.268 & 0.264--0.279 \\
    $f_{GBR \rightarrow Nama}$ & Ancestry proportion from Europeans to Nama 10 generations ago & 0.153 & 0.148--0.156 \\
    $m_{stems}$ & Stem 1--stem 2 migration rate & $0$ & fixed \\
    $m_{stem2-Nama}$ & Stem 2--Nama migration rate & $4.33\times10^{-5}$ & $4.91\times10^{-5}$--$5.92\times10^{-5}$ \\
    $m_{stem2-MSL}$ & Stem 2--Mende migration rate & $11.3\times10^{-5}$ & $12.4\times10^{-5}$--$14.4\times10^{-5}$ \\
    $m_{stem2-EA}$ & Stem 2--East Africa migration rate & $2.77\times10^{-5}$ & $3.04\times10^{-5}$--$3.95\times10^{-5}$ \\
    \bottomrule
\end{tabular}
\end{table}

@@

\begin{table}[ht]
\caption{
    \label{tab:supp-merger-without-stem-migration}
    \textbf{Best-fit parameters from the Merger-Without-Stem-Migration model.}
    Inferred values are scaled to physical units assuming a generation time of
    29 years. This model gave a log-likelihood of -107,652.
}
\centering
\begin{tabular}[t]{rP{8cm}cc}
    \toprule
    Parameter & Description & Value & 95\% CIs\\
    \midrule
    $N_e$ & Ancestral effective population size & 11300 & 10100--11290 \\
    $N_{stem1}$ & Size of stem 1 lineage between stem 1--stem 2 split and stem 1E--stem 1S split & 113 & 113--606 \\
    $N_{stem2}$ & Size of stem 2 lineage & 24780 & 26500--35060 \\
    $N_{Nama_0}$ & Initial Nama and stem 1S size & 13080 & 11310--12910 \\
    $N_{Nama_F}$ & Final Nama size & 224 & 223--238 \\
    $N_{MSL_0}$ & Initial Mende size & 11870 & 10280--11630 \\
    $N_{MSL_F}$ & Final Mende size & 25570 & 25720--30180 \\
    $N_{EA}$ & Size of East African and stem 1E branch & 9110 & 8680--9140 \\
    $N_{Gumuz_F}$ & Final Gumuz size & 3370 & 3270--3470 \\
    $N_{EP}$ & East African agriculturist size & 13550 & 13120--13690 \\
    $N_{GBR_0}$ & Initial British size & 927 & 920--963 \\
    $N_{GBR_F}$ & Final British size & 12050 & 11790--12430 \\
    $N_{Neand}$ & Neanderthal size & 1940 & 1770--2110 \\
    $T_{stems}$ & Stem split time (years) & 411700 & 381400--410700 \\
    $T_{stem1}$ & Stem 1 split time into stem 1E and stem 1S (years) & 355400 & 154300--320400 \\
    $m_{Nama-MSL}$ & Nama--Mende symmetric migration rate & $0.361\times10^{-5}$ & $0.205\times10^{-5}$--$0.697\times10^{-5}$ \\
    $m_{Nama-EA}$ & Nama--East Africa symmetric migration rate & $4.04\times10^{-5}$ & $3.90\times10^{-5}$--$4.42\times10^{-5}$ \\
    $m_{MSL-EA}$ & Mende--East Africa migration rate & $19.3\times10^{-5}$ & $19.8\times10^{-5}$--$20.8\times10^{-5}$ \\
    $m_{EA-GBR}$ & East Africa--Europe migration rate & $3.76\times10^{-5}$ & $3.34\times10^{-5}$--$3.95\times10^{-5}$ \\
    $m_{EA-EA}$ & Intra-East Africa migration rate & $37.2\times10^{-5}$ & $35.2\times10^{-5}$--$39.6\times10^{-5}$ \\
    $f_{GBR \rightarrow EP}$ & Ancestry proportion of East African agriculturalists from GBR 12ka ($1-f$ from Gumuz) & 0.648 & 0.641--0.661 \\
    $f_{EP \rightarrow Nama}$ & Ancestry proportion from EA pastoralists to Nama 2ka & 0.258 & 0.245--0.264 \\
    $f_{GBR \rightarrow Nama}$ & Ancestry proportion from Europeans to Nama 10 generations ago & 0.156 & 0.152--0.161 \\
    $m_{stems}$ & Stem 1--stem 2 migration rate & $0$ & fixed \\
    $T_{Nama}$ & Time of Nama merger event & 115400 & 101400--116800 \\
    $f_{stem 2 \rightarrow Nama}$ & Proportion of stem 2 ancestry making up initial Nama lineage ($1-f$ from stem 1S) & 0.693 & 0.706--0.769 \\
    $T_{EA}$ & Time of East Africa merger event & 92940 & 94500--10140 \\
    $f_{stem 2 \rightarrow EA}$ & Proportion of stem 2 ancestry making up initial East Africa lineage ($1-f$ from stem 1E) & 0.502 & 0.510--0.564 \\
    $T_{MSL}$ & Time of secondary admixture from stem 2 to Mende & 23490 & 22920--25510 \\
    $f_{stem 2 \rightarrow MSL}$ & Proportion of ancestry from secondary stem 2 admixture to Mende & 0.170 & 0.174--0.196 \\
    \bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}[ht]
\caption{
    \label{tab:supp-continuous-migration-no-mig}
    \textbf{Best-fit parameters from the Continuous-Migration model without stem migration.}
    Inferred values are scaled to physical units assuming a generation time of
    29 years. This model gave a log-likelihood of -126,644. This model allows for
    continuous migration between Stem 2 and contemporary populations, but disallows
    migration between Stem 2 and Stem 1, which later splits into branches leading
    to South, East, and West African populations.
}
\centering
\begin{tabular}[t]{rP{8cm}cc}
    \toprule
    Parameter & Description & Value & 95\% CIs \\
    \midrule
    $N_e$ & Ancestral effective population size & 10980 & 10810--11260 \\
    $N_{stem1}$ & Size of stem 1 lineage between Neanderthal and Nama splits & 13980 & 13930--15330 \\
    $N_{stem2}$ & Size of stem 2 lineage & 10390 & 9780--11250 \\
    $N_{Nama_0}$ & Initial Nama size & 11240 & 10760--11280 \\
    $N_{Nama_F}$ & Final Nama size & 221 & 216--226 \\
    $N_{MSL_0}$ & Initial Mende size & 10810 & 10510--11090 \\
    $N_{MSL_F}$ & Final Mende size & 25080 & 24050--25780 \\
    $N_{EA}$ & Size of East African branch & 7130 & 6970--7200 \\
    $N_{Gumuz_F}$ & Final Gumuz size & 3770 & 2650--3860 \\
    $N_{EP}$ & East African agriculturist size & 13070 & 12830--13250 \\
    $N_{GBR_0}$ & Initial British size & 946 & 931--964 \\
    $N_{GBR_F}$ & Final British size & 11560 & 11320--11760 \\
    $N_{Neand}$ & Neanderthal size & 2290 & 2140--2450 \\
    $T_{stems}$ & Stem split time (years) & 459700 & 446600--463300 \\
    $T_{Nama}$ & Nama split time (years) & 145400 & 137300--146000 \\
    $m_{Nama-MSL}$ & Nama--Mende symmetric migration rate & $1.46\times10^{-5}$ & $1.36\times10^{-5}$--$1.81\times10^{-5}$ \\
    $m_{Nama-EA}$ & Nama--East Africa symmetric migration rate & $4.22\times10^{-5}$ & $4.08\times10^{-5}$--$4.60\times10^{-5}$ \\
    $m_{MSL-EA}$ & Mende--East Africa migration rate & $20.8\times10^{-5}$ & $20.7\times10^{-5}$--$21.3\times10^{-5}$ \\
    $m_{EA-GBR}$ & East Africa--Europe migration rate & $4.36\times10^{-5}$ & $4.19\times10^{-5}$--$4.58\times10^{-5}$ \\
    $m_{EA-EA}$ & Intra-East Africa migration rate & $35.8\times10^{-5}$ & $34.6\times10^{-5}$--$37.0\times10^{-5}$ \\
    $f_{GBR \rightarrow EP}$ & Ancestry proportion of East African agriculturalists from GBR 12ka ($1-f$ from Gumuz) & 0.651 & 0.644--0.660 \\
    $f_{EP \rightarrow Nama}$ & Ancestry proportion from EA pastoralists to Nama 2ka & 0.271 & 0.264--0.279 \\
    $f_{GBR \rightarrow Nama}$ & Ancestry proportion from Europeans to Nama 10 generations ago & 0.153 & 0.148--0.156 \\
    $m_{stems}$ & Stem 1--stem 2 migration rate & $0$ & fixed \\
    $m_{stem2-Nama}$ & Stem 2--Nama migration rate & $5.63\times10^{-5}$ & $4.91\times10^{-5}$--$5.92\times10^{-5}$ \\
    $m_{stem2-MSL}$ & Stem 2--Mende migration rate & $14.2\times10^{-5}$ & $12.4\times10^{-5}$--$14.4\times10^{-5}$ \\
    $m_{stem2-EA}$ & Stem 2--East Africa migration rate & $3.82\times10^{-5}$ & $3.04\times10^{-5}$--$3.95\times10^{-5}$ \\
    \bottomrule
\end{tabular}
\end{table}

@@

\begin{table}[ht]
\caption{
    \label{tab:supp-merger-without-stem-migration}
    \textbf{Best-fit parameters from the Merger-Without-Stem-Migration model.}
    Inferred values are scaled to physical units assuming a generation time of
    29 years. This model gave a log-likelihood of -107,652.
}
\centering
\begin{tabular}[t]{rP{8cm}cc}
    \toprule
    Parameter & Description & Value & 95\% CIs\\
    \midrule
    $N_e$ & Ancestral effective population size & 11410 & 10100--11290 \\
    $N_{stem1}$ & Size of stem 1 lineage between stem 1--stem 2 split and stem 1E--stem 1S split & 102 & 113--606 \\
    $N_{stem2}$ & Size of stem 2 lineage & 24720 & 26500--35060 \\
    $N_{Nama_0}$ & Initial Nama and stem 1S size & 13180 & 11310--12910 \\
    $N_{Nama_F}$ & Final Nama size & 224 & 223--238 \\
    $N_{MSL_0}$ & Initial Mende size & 11760 & 10280--11630 \\
    $N_{MSL_F}$ & Final Mende size & 25770 & 25720--30180 \\
    $N_{EA}$ & Size of East African and stem 1E branch & 9190 & 8680--9140 \\
    $N_{Gumuz_F}$ & Final Gumuz size & 3360 & 3270--3470 \\
    $N_{EP}$ & East African agriculturist size & 13590 & 13120--13690 \\
    $N_{GBR_0}$ & Initial British size & 936 & 920--963 \\
    $N_{GBR_F}$ & Final British size & 12080 & 11790--12430 \\
    $N_{Neand}$ & Neanderthal size & 1950 & 1770--2110 \\
    $T_{stems}$ & Stem split time (years) & 415100 & 381400--410700 \\
    $T_{stem1}$ & Stem 1 split time into stem 1E and stem 1S (years) & 360700 & 154300--320400 \\
    $m_{Nama-MSL}$ & Nama--Mende symmetric migration rate & $0.523\times10^{-5}$ & $0.205\times10^{-5}$--$0.697\times10^{-5}$ \\
    $m_{Nama-EA}$ & Nama--East Africa symmetric migration rate & $4.09\times10^{-5}$ & $3.90\times10^{-5}$--$4.42\times10^{-5}$ \\
    $m_{MSL-EA}$ & Mende--East Africa migration rate & $19.5\times10^{-5}$ & $19.8\times10^{-5}$--$20.8\times10^{-5}$ \\
    $m_{EA-GBR}$ & East Africa--Europe migration rate & $3.74\times10^{-5}$ & $3.34\times10^{-5}$--$3.95\times10^{-5}$ \\
    $m_{EA-EA}$ & Intra-East Africa migration rate & $30.7\times10^{-5}$ & $35.2\times10^{-5}$--$39.6\times10^{-5}$ \\
    $f_{GBR \rightarrow EP}$ & Ancestry proportion of East African agriculturalists from GBR 12ka ($1-f$ from Gumuz) & 0.648 & 0.641--0.661 \\
    $f_{EP \rightarrow Nama}$ & Ancestry proportion from EA pastoralists to Nama 2ka & 0.259 & 0.245--0.264 \\
    $f_{GBR \rightarrow Nama}$ & Ancestry proportion from Europeans to Nama 10 generations ago & 0.156 & 0.152--0.161 \\
    $m_{stems}$ & Stem 1--stem 2 migration rate & $0$ & fixed \\
    $T_{Nama}$ & Time of Nama merger event & 118200 & 101400--116800 \\
    $f_{stem 2 \rightarrow Nama}$ & Proportion of stem 2 ancestry making up initial Nama lineage ($1-f$ from stem 1S) & 0.693 & 0.706--0.769 \\
    $T_{EA}$ & Time of East Africa merger event & 94300 & 94500--101400 \\
    $f_{stem 2 \rightarrow EA}$ & Proportion of stem 2 ancestry making up initial East Africa lineage ($1-f$ from stem 1E) & 0.497 & 0.510--0.564 \\
    $T_{MSL}$ & Time of secondary admixture from stem 2 to Mende & 23890 & 22920--25510 \\
    $f_{stem 2 \rightarrow MSL}$ & Proportion of ancestry from secondary stem 2 admixture to Mende & 0.171 & 0.174--0.196 \\
    \bottomrule
\end{tabular}
\end{table}
